---
output:
  pdf_document: default
  html_document: default
---
# HW2

```{r}
library(tidyverse)
library(tidymodels)
library(readr)
library(yardstick)
```

Import dataset
```{r}
abalone <- read_csv(file = 'abalone.csv')
view(abalone)
```

# Q1
```{r}
age <- abalone$rings + 1.5
abalone_new <- cbind(abalone, age)
view(abalone_new)
```
```{r}
ggplot(data = abalone_new, aes(x = age)) + geom_histogram()
```
The distribution of age variable seems approximately normal to me. The data is right skewed.

# Q2
```{r}
set.seed(1234)
abalone_split <- initial_split(abalone_new, prop = 0.75, strata = age)
abalone_training <- training(abalone_split)
abalone_testing <- testing(abalone_split)
```

# Q3
```{r}
abalone_training_2 <- select(abalone_training, -rings)
recipe <- recipe(age ~ ., data = abalone_training_2) %>% step_dummy(type)

recipe <- step_interact(recipe, terms = ~ shucked_weight : starts_with('type'))
recipe <- step_interact(recipe, terms = ~ diameter : longest_shell)
recipe <- step_interact(recipe, terms = ~ shell_weight : shucked_weight)

recipe <- step_center(recipe, longest_shell, diameter, height, whole_weight, shucked_weight,
                      viscera_weight, shell_weight)
recipe <- step_scale(recipe, longest_shell, diameter, height, whole_weight, shucked_weight,
                     viscera_weight, shell_weight)
```
Rings variable should not be included because age variable is directly calculated from rings variable(linear relationship), so it is meaningless to include age while predicting rings.

# Q4
```{r}
lm_model <- linear_reg() %>% set_engine('lm') %>% set_mode('regression')
lm_model
```

# Q5
```{r}
lm_workflow <- workflow() %>% add_model(lm_model) %>% add_recipe(recipe)
```

# Q6
```{r}
lm_fit <- fit(lm_workflow, abalone_training_2)

type = c('F')
longest_shell = c(0.5)
diameter = c(0.1)
height = c(0.3)
whole_weight = c(4)
shucked_weight = c(1)
viscera_weight = c(2)
shell_weight = c(1)

predict_abalone <- data.frame(type, longest_shell, diameter, height, whole_weight,
                              shucked_weight, viscera_weight, shell_weight)
predict(lm_fit, new_data = predict_abalone)
```

# Q7
```{r}
abalone_metric <- metric_set(rsq, rmse, mae)
abalone_training_3 <- select(abalone_training_2, -age)
abalone_training_pred <- predict(lm_fit, new_data = abalone_training_3)
abalone_training_age <- select(abalone_training_2, age)
abalone_training_combined <- bind_cols(abalone_training_pred, abalone_training_age)
abalone_training_combined

abalone_metric(abalone_training_combined, truth = age, estimate = .pred)
```
R-squared: 0.55627
RMSE: 2.13766
MAE: 1.54726
An R-square value of 0.55627 means that about 55.63% of the variation in age can be explained by the predictors.
